Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2019-10-02 manuscript/manuscript.tex

While it challenging to apply temporal methods to natural populations there is
a lot of promise for these approaches
\parencite{Bergland2014-ij,Machado2018-cs}. Efforts to estimate and quantify
the impact of linked selection in humans and \emph{Drosophila melanogaster}
have suggested that XXX to XXX of allele frequency change over long time
periods is driven by selection \parencite{}. Thus there is reason to be hopeful
that we could detect this from temporal data, which would help to resolve the
timescales that linked selection act over. In our reanalysis of the
\textcite{Barghi2019-qy} study, we find evidence of complex linked selection
dynamics, with selection pressures flipping over time due to either
environmental change, the breakup of epistatic combinations or advantageous
haplotypes. Such patterns would be completely obscured in samples only from
contemporary populations, thus we can hope to have a much richer picture of
linked selection as temporal sequencing becomes more common.

>>>>

While it challenging to apply temporal methods to natural populations there is
a lot of promise for these approaches
\parencite{Bergland2014-ij,Machado2018-cs}. Efforts to estimate the quantify
the impact of linked selection in have suggested that XXX to XXX of allele
frequency change over long time periods is driven by selection
\parencite{Mcvicker,Comeron,Elyashiv2016-vt,Russ,Coop}. Thus there is reason to
be hopeful that we could detect this from temporal data, which would help to
resolve the time-scales that linked selection act over. In our reanalysis of
the \textcite{Barghi2019-qy} study, we find evidence of complex linked
selection dynamics, with selection pressures flipping over time due to either
environmental change, the breakup of epistatic combinations or advantageous
haplotypes. Such patterns would be completely obscured in samples only from
contemporary populations, thus we can hope to have a much richer picture of
linked selection as temporal sequencing becomes more common.
